---
title: "Exploring the BRFSS data"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
```

### Load data

Make sure your data and R Markdown files are in the same directory. When loaded
your data file will be called `brfss2013`. Delete this note when before you submit 
your work. 

```{r load-data}
load("brfss2013.RData")
```





* * *

## Part 1: Data


* * *

## Part 2: Research questions

**Research quesion 1:**

Is working out in the past 30 days is associated with the frequency of a person being nerouvs during previous month difference between men and femail?


```{r}

#preparing the data
Nervous_sex_exercise <- brfss2013 %>% select(sex,exerany2, misnervs)

Nervous_sex_exercise <- Nervous_sex_exercise %>% filter(!is.na(misnervs),!is.na(sex))

#summarise by sex(how many males and femails in the prepared set)

Nervous_sex_exercise_Sex_prop <- Nervous_sex_exercise %>% group_by(sex) %>% summarise(count= n()) %>% mutate(perc=count/sum(count))

Nervous_sex_exercise_Sex_prop

#percentages of people in groups of 

Nervous_sex_exercise <- Nervous_sex_exercise %>% group_by(misnervs,sex) %>% summarise(count= n())  %>% mutate(perc=count/sum(count)) 

#stacked barchart for number of people for different sexes being nervious a particular proportion of the past 30 days

Nervous_sex_exercise_plot <- ggplot(Nervous_sex_exercise, aes(x=misnervs, y=perc, fill= sex ))+geom_bar(stat="identity")

Nervous_sex_exercise_plot + geom_hline(yintercept=0.59)



Nervous_sex_exercise <- Nervous_sex_exercise %>% mutate(diff_from_Marginal=ifelse(sex=="Male",Nervous_sex_exercise_Sex_prop$perc[1],Nervous_sex_exercise_Sex_prop$perc[2]	)-perc)


ggplot(Nervous_sex_exercise, aes(fill=sex, y=diff_from_Marginal, x=misnervs)) + geom_bar(position="dodge", stat="identity")

##ggplot replace count with percentage in geom_bar→https://stackoverflow.com/questions/24776200/ggplot-replace-count-with-percentage-in-geom-bar/48602277

 
#QUESTION: How do I construct an experiment which will help me answer the question about "Are Men having in general more stresfull life than women". From what I know I would need to choose a random group of people and assign "sex" randomly to each of the participants, and then I will see what happens. But you can't change sexes of your participants. So what should I do?
```

It looks like in US men are more likely to have a nervious day then women.

**Research quesion 2:**

Is working out in the past 30 days is associated with number of days you mentaly feal not good and what is the difference between men and femail?



**Research quesion 3:**


* * *

## Part 3: Exploratory data analysis

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button (green button with orange arrow) above. Make sure that your code is visible
in the project you submit. Delete this note when before you submit your work.

**Research quesion 1:**

```{r}

```



**Research quesion 2:**

```{r}

```



**Research quesion 3:**

```{r}

```

