---
title: "Exploring the BRFSS data"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
```

### Load data

Make sure your data and R Markdown files are in the same directory. When loaded
your data file will be called `brfss2013`. Delete this note when before you submit 
your work. 

```{r load-data}
load("brfss2013.RData")
```





* * *

## Part 1: Data


* * *

## Part 2: Research questions

**Research quesion 1:**

Is working out in the past 30 days is associated with the frequency of a person being nerouvs during previous month difference between men and femail?


```{r}

Nervous_sex_exercise <- brfss2013 %>% select(sex,exerany2, misnervs)

Nervous_sex_exercise %>% filter(!is.na(misnervs),!is.na(sex) ) %>% group_by(sex) %>% summarise(count= n())

Nervous_sex_exercise %>% filter(!is.na(sex)) %>% group_by(misnervs) %>% summarise(x=sum(sex))

test <- Nervous_sex_exercise %>% filter(!is.na(misnervs),!is.na(sex) ) %>% group_by(misnervs,sex) %>% summarise(count= n())  %>% mutate(perc=count/sum(count)) %>% arrange

Nervous_sex_exercise %>% filter(!is.na(misnervs),!is.na(sex)) %>% ggplot(aes(x=misnervs, fill=sex))+geom_bar()


ggplot(test, aes(x=misnervs, y=perc, fill= sex ))+geom_bar(stat="identity")

test$misnervs

##ggplot replace count with percentage in geom_bar→https://stackoverflow.com/questions/24776200/ggplot-replace-count-with-percentage-in-geom-bar/48602277

Nervous_sex_exercise %>% filter(!is.na(sex),!is.na(misnervs) ) %>% group_by(sex) %>% summarise(x=n()) %>% mutate(y=x/sum(x))


```


```{r}

##
ggplot(test, aes(x=misnervs, y=perc, fill= sex ))+geom_bar(stat="identity")
ggplot(test, aes(x=misnervs))+geom_histogram()
```


**Research quesion 2:**

**Research quesion 3:**


* * *

## Part 3: Exploratory data analysis

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button (green button with orange arrow) above. Make sure that your code is visible
in the project you submit. Delete this note when before you submit your work.

**Research quesion 1:**

```{r}

```



**Research quesion 2:**

```{r}

```



**Research quesion 3:**

```{r}

```

